### 2018-08-28 case_for_support.tex
Finished two partners

  \vspace{2mm}
  \noindent
  Our work funded through the round of GCRF funding has demonstrated our ability to successfully collaborate with external organisations. Our current external partners have a regional, as opposed to national or international, presence. While working with such small-to-medium size partners has proven beneficial in terms of our developing good working relationships, our ultimate goal is to also work with partners with a national presence within Thailand. Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a broad variety of external partners to work with our team and their students.

  For this capacity-building project, we request funds to expand upon our first GCRF-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the first phase. We also request funding to continue our collaboration with Thanapiriya. All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support). At the end of the first 12 months, however, we plan to hold a networking event to attract other external partners.

>>>>

  \vspace{2mm}
  \noindent
  Our work funded through the first round of GCRF funding has demonstrated our ability to successfully collaborate with external organisations. Our current external partners have a regional, as opposed to national or international, presence. While working with such small-to-medium size partners has proven beneficial in terms of our developing good working relationships, our ultimate goal is to also work with partners with a national presence within Thailand. Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a broad variety of external partners to work with our team and their students.

  For this capacity-building project, we request funds to expand upon our first GCRF-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the first phase. We also request funding to continue our collaboration with Thanapiriya. All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support). At the end of the first 12 months, however, we will hold a networking event to attract other external partners. Below, we provide a brief description of the external partners and their data needs:

  \begin{itemize}
  \item {\bf Thai AirAsia} is part of the AirAsia group, which is the largest budget airline operating in South East Asia. They are renowned among the air industry for their high levels of aircraft utility (i.e., maximising the time a plane is in the air, and thus generating revenue). A barrier to achieving even higher levels of aircraft utility is the grounding of aircraft while they wait for the delivery of spare parts from various warehouses. This waiting could be reduced if AirAsia were able to predict when parts were likely to require replacement, and then act upon this when the aircraft was located at an airport with a parts warehouse. AirAsia engineers will share their flight data with our team so that we can adapt the techniques we have developed to identify rare sources in astronomy to better predict rare instances where parts require replacement. To assist with this development, Thai AirAsia have offered to host the students working on the project on a work-experience placement.
  \item {\bf Thaweeyont} is a chain of bricks-and-mortar stores that specialise in electronic household appliances, furniture and motorcycles/scooters. They have expanded rapidly over the past decade, and are now looking to move into more locations. A problem they face when opening new stores is how to predict the types of customer (sex, age, dispoable income, etc.) that are likely to visit the new store, which has knock-on effects on how to stock the new store. Thaweeyont would like a work with small group of students and researchers to investigate how we can adapt the work conducted during the first phase of our GCRF project (see Thanapiriya) to characterize their customers on a branch-by-branch basis and predict appropriate levels of stock.
  \item {\bf Deevana Hotel Group} is a group of eight hotels based in the south of Thailand.
\end{itemize}
